Notebook of learning from ensemble labels

### 2021-06-01 docs/notebook_learn_dl_ensemble.Rmd
Modify the default params for coteaching

```
python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200 --resume 'results/dl/resume/interim.pth' --save_freq 5
```

>>>>

```
python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200 --save_freq 5 --resume 'results/dl/resume/interim.pth'
```
